\documentclass{llncs}

\begin{document}
\title{Multi-Agent Programming Contest 2012\\Participation Registration Template}
\author{}
\institute{}
\maketitle

\begin{abstract}
  Please follow the given template structure for your submission by
  answering the questions as concisely as possible, not exceeding the
  total of \textbf{4} pages. It is vital to explain in this submission
  how are you using a multiagent approach.

%   a \textit{description} of the system, the
%   methodology/tools/infrastructure used and the (team) strategy that
%   you plan to use in the contest.

%   Please send your submission by email to J\"urgen Dix
%   (\url{dix@tu-clausthal.de}) no later than August 9th. If
%   modifications are necessary, we will directly ask you to submit a
%   final version on August 16th.
\end{abstract}


\section*{Introduction}

Note: the information you provide in this section will be made available
to all participants. We will put it on the homepage.

\begin{enumerate}
\item What is the name of your team?
\item Who are the members of your team? Please provide names, academic
  degrees and institutions.
%\item Which platform/architecture/programming language do you use? (in sec 3)
\item Who is the main-contact?
\item How much time (man hours) will you have invested (approximately)
  until the tournament?
\end{enumerate}

\section*{System Analysis and Design}

\begin{enumerate}
  %\item How is your system  specified and designed?
  \item Briefly, what is the main strategy of the team?
  \item Will you use any existing multi-agent system
  methodology such as Prometheus, O-MaSE, or Tropos?
 \item Do you plan to distribute your agents on several machines?
 \item Is your solution based on the centralisation of
   coordination/information on a specific agent? Conversely if you
   plan a decentralised solution, which strategy do you plan to use?
\item Describe the communication strategy in the agent team. Can you
   estimate the communication complexity in your approach?
 \item Describe the team coordination strategy (if any)
 \item How are the following agent features implemented:
   \emph{autonomy}, \emph{proactiveness}, \emph{reactiveness}?
% Is your system a truly \textbf{multi}-agent system or
%   rather a centralised system in disguise?
\end{enumerate}


\section*{Software Architecture}

\begin{enumerate}
\item Which programming language do you plan to use to implement the
  multi-agent system? (e.g. 2APL, Jason, Jadex, JIAC, Java, ...)
% \item How would you map the designed architecture (both multi-agent
%   and individual agent architectures) to programming codes, i.e., how
%   would you implement specific agent-oriented concepts and designed
%   artifacts using the programming language?
\item Which development platform and tools are you planning to use?
\item Which runtime platform and tools are you planning to use?
  (e.g. Jade, AgentScape, simply Java, ....)
\item Which algorithms will be used?
\end{enumerate}
Please explain the reasons for your answers.

% \section{Agent team strategy}

% Please address the following points, or at least comment if not applicable:

% \begin{enumerate}
%     \item Describe the navigation algorithms:
%         \begin{itemize}
%             \item obstacle avoiding
%             \item strategy for finding and herding cows
%             \item opponent blocking
%         \end{itemize}
%     \item Describe the team coordination strategy (if any)
%     \item Does your team strategy use some distributed optimization
%         technique w.r.t. e.g.  minimizing distances walked by the
%         agents?
%     \item Describe and discuss the information exchanged (and shared) in
%         the agent team.
%     \item Describe the communication strategy in the agent team. Can you
%         estimate the communication complexity in your approach?
%     \item Did your system do some background processing? Under background
%         processing we understand some computation which happened while agents of
%         the team were \textit{idle}, i.e. between sending an action
%         message to the simulation server and receiving a perception
%         message for the subsequent simulation step.
%     \item Possibly discuss additional technical details of your system like
%         e.g. failure/crash recovery and alike.
% \end{enumerate}



\end{document}

